Making Sequential Programs Deterministic

### 2019-04-05 java-design.tex
todo map subtyping relationship

The JDK implements \<LinkedHashSet> as a subclass of \<HashMap>\todo{should
  this be HashSet?  It's not true as written.}
in order to inherit parts of \<HashMap>'s implementation.
\todo{Talk about this design choice. Josh Bloch's book: "If the code surrounding the first declaration depended on LinkedHashSet's ordering policy,
    then it would be incorrect to substitute HashSet for LinkedHashSet in the declaration, because HashSet makes no guarantee concerning iteration order."} 
\todo{The above is not clear.  What are the consequences for our
  implementation.  What goes wrong or is hard to annotate or is surprising?
  I'm not sure what is the point of this paragraph.}

>>>>

The JDK implements \<LinkedHashMap> as a subclass of \<HashMap>
in order to inherit parts of \<HashMap>'s implementation.
%\todo{Talk about this design choice. Josh Bloch's book: "If the code surrounding the first declaration depended on LinkedHashSet's ordering policy, then it would be incorrect to substitute HashSet for LinkedHashSet in the declaration, because HashSet makes no guarantee concerning iteration order."} 
%\todo{The above is not clear.  What are the consequences for our
%  implementation.  What goes wrong or is hard to annotate or is surprising?
%  I'm not sure what is the point of this paragraph.}
\todo{From the discussion in this section, it is clear that \<LinkedHashMap> and \<HashMap> do not
have a subtyping relationship with respect to their determinism types. We looked at the implementation of
these two classes in the JDK and found that \<LinkedHashMap> doesn't reuse code that corresponds to 
iterating over its keys or values with \<HashMap>.}
